
\begin{center}
\textbf{Acknowledgements}
\end{center}

First and foremost, I would like to thank Deepak Chauhan and the branch he works for, FAA NextGen Surveillance Branch (ANG-C33) for funding the research for this thesis with the FAA Cooperative Agreement No. 15-G-001, which was awarded to Rowan University.

I would also like to thank Andrew Fabian of the FAA NextGen Unmanned Aircraft Systems Branch, ANG-C35 (formerly the Modeling and Simulation Branch, ANG-C55), for his expertise and insight into flight mechanics, bearing calculations, and overall algorithm derivation expertise. This work would not have been able to be completed without you, and I sincerely thank you for that and being a good friend and coworker.

I am very fortunate and grateful to Mike Paglione, who guided this project and research from the FAA standpoint. You are a great manager, and I am thankful that I had the privilege to work under you, and to learn so much from you and others in the branch.

To Dr. Bouaynaya, thank you for your patience in completing this thesis, and for the expertise and knowledge in support of this work. I learned so much from your teachings, and I cannot thank you enough for everything. 

Not least of all, I owe thanks to my wife, stepson, mentors, and friends for their support and patience as I completed this thesis. I cannot name everyone, as it would take a lifetime to write, and too many pages to fill, but I want you all to know how thankful I am. Thank you everyone.


\newpage